\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-25 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
modification partie agrégation

Current data are available at the 10-digit level for products (HS10) for some specific years. The results reported here rely on exploiting data over the years 1997-1999 and 2001-2019.\footnote{Theoretically, they should be available from 1989, which is already smaller than our full sample starting in 1974. Because of the COVID situation, it was only possible to get access to the years 1997-1999 and 2001-2019.} \textbf{REPRENDRE CES RESULTATS PB SUR VESSEL LP. }

@@

Yet, as Table \ref{tab:baseline10} and 	Figure \ref{fig:robustness_to_agregation} show, the results are similar when using 10-digit product and 5-digit products.

>>>>

Current data are available at the 10-digit level for products (HS10) for some specific years. The results reported here rely on exploiting data from 2005 to 2019. This period is obviously smaller than our main sample, due to two main issues. Firstly, we could only access the years 1997-1999 and 2001-2019.\footnote{Theoretically, they should be available from 1989, which is already smaller than our full sample starting in 1974. Because of the COVID situation, it was only possible to get access to the years 1997-1999 and 2001-2019.} Secondly, for the years 1997-1999 and 2001-2005, compatibility issues between Census and Hummels' data prevented reliable comparisons.

@@

Yet, as Table \ref{tab:baseline10} and 	Figure \ref{fig:robustness_to_agregation} show, the results are very similar when using 10-digit product and 5-digit products. If anything, the $\beta$ seems on average slightly higher when estimated based on a 3 (sector)-10(product) database, indicating a (small) downward bias in our estimates of additive costs. But overall, no major difference arises both regarding levels and trends - results are especially very close for the Air transportation mode. This has important implications for the exercise performed in section \ref{sec:theory}: welfare gains computations should not be significantly affected by our use of 5 (sector)-5 (product) digit data. This is consistent with e.g. \citet{Giri_et_al2021}, who show that sectoral heterogeneity does not always lead to an increase in the gains from trade.
